\renewcommand{\bibname}{REFERENCES}
\begin{thebibliography}{99}
\sloppy
\addcontentsline{toc}{chapter}{References}
    \bibitem{python} Python Software Foundation. \textit{Python 3 Documentation}. Available at: \url{https://docs.python.org/3/}
    \bibitem{tensorflow} TensorFlow Developers. \textit{TensorFlow Documentation}. Available at: \url{https://www.tensorflow.org/api_docs}
    \bibitem{keras} Keras Team. \textit{Keras: Deep Learning for Humans}. Available at: \url{https://keras.io/api/}
    \bibitem{flask} Pallets Projects. \textit{Flask Web Development Documentation}. Available at: \url{https://flask.palletsprojects.com/}
    \bibitem{opencv} OpenCV Team. \textit{OpenCV Documentation}. Available at: \url{https://docs.opencv.org/}
    \bibitem{sklearn} Scikit-Learn Developers. \textit{Machine Learning in Python}. Available at: \url{https://scikit-learn.org/stable/}
    \bibitem{numpy} NumPy Developers. \textit{NumPy Documentation}. Available at: \url{https://numpy.org/doc/}
    \bibitem{pandas} Pandas Development Team. \textit{Pandas Data Analysis Library}. Available at: \url{https://pandas.pydata.org/docs/}
    \bibitem{matplotlib} Matplotlib Development Team. \textit{Matplotlib: Visualization with Python}. Available at: \url{https://matplotlib.org/stable/contents.html}
    \bibitem{google_teachable} Google. \textit{Teachable Machine Documentation}. Available at: \url{https://teachablemachine.withgoogle.com/faq}
    \bibitem{google_stitch} Google. \textit{Google Stitch / Material Design Guidelines}. Available at: \url{https://m3.material.io/}
    \bibitem{chollet} Chollet, F. \textit{Deep Learning with Python}. 2nd ed. Manning Publications, 2021.
    \bibitem{geron} Géron, A. \textit{Hands-On Machine Learning with Scikit-Learn, Keras, and TensorFlow}. 3rd ed. O'Reilly Media, 2022.
\end{thebibliography}
